The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-17 src/tex/ms.tex
[showyourwork] overleaf sync
temporary fix for mnras float error
[showyourwork]

%%%%%%%%%%%%%%%%%% FIGURE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \script{half_mass_radius_gas.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_gas_size.pdf}
        \caption{
            Half mass radius of the cold gas as a function of time. Sudden increase around 2, 3 and 9 Gyr clearly signify the gas rich merger events this galaxy undergoes.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\bibliography{astro-ph.bib}

>>>>

\begin{figure}
    \script{half_mass_radius_gas.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/279e12_gas_size.pdf}
        \caption{
            Half mass radius of the cold gas as a function of time. The sharp increases in the cold gas size around 2 Gyr and 9 Gyr indicate the influence of massive gas rich merger events on the galaxy. The addition of fresh cold gass leads to a sudden increase in cold gas half mass size.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}

\begin{figure}
    \script{merger_ratio.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_merger_ratio_gas.pdf}
        \caption{
            Half mass radius of the cold gas as a function of time. The sharp increases in the cold gas size around 2 Gyr and 9 Gyr indicate the influence of massive gas rich merger events on the galaxy. The addition of fresh cold gass leads to a sudden increase in cold gas half mass size.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}

@@

\bibliography{bib.bib}
